Title of the document here

### 2015-01-28 rmtw/assignment_1/assignment_1.tex
fixed compilation error
Started methodology section

The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.

The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.

\newline

@@

\begin{tabular}{| l | r | c |}
	\hline
	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
	Occupation & RQ1, SQ1 & \\ \hline
	Experience & RQ1, SQ1 & \\ \hline
	Preferred Language & RQ1, SQ2 & \\ \hline
	Least Preferred Language & RQ1, SQ2& \\  \hline
	Working Language & RQ1, SQ2 & \\ 
	\hline
	\end{tabular}
%------------------------------------------------------------------------- 
\Section{Methodology}

* Describe  and explain the research  strategy (i.e.  Survey/Questionnaire)
and investigation methods that  will  be  used  for the study.  Motivate  your  
choice  of  survey/questionnaire  using relevant  references.

The main purpose of our study is to discover differences between the perceived readability of code. To discover an answer to this question, we would likely collect data and opinions from a broad population. As such, we most likely need to perform a research survey. This is reinforced by Easterbrook et. al \cite{easterbrook2008selecting} who stated ``Survey research is used to identify the characteristics of a broad population of individuals''.

 case-control design - ``asks each participant about several related issues in 
order to establish whether a correlation exists between them,'' \cite{easterbrook2008selecting}

We will use a survey/questionnaire to collect the data.
Sampling - ID a small subset of the entire population

* Describe  data  collection  procedures, sampling  method(s),  number  of  
subjects, response  rate  etc.

Random sampling from 200 people(guess). Sample 10\%, collect online via survey, Response rate of 15/20 (75\%)

Sampling bias - What we might face, how we overcome. State which threats and how they were minimised

* Create  questions for your  survey  (include  the questions in  your  report)
%Table goes here
* Describe  the population  and size  of  population

The population will be software developers in the SEM program. This includes teachers, students, professionals and hobbyists. Lets say the sample is 20 persons from the whole of SEM, 1st, 2nd, 3rd and staff.

\cite{easterbrook2008selecting} - ``A major challenge in survey research is to control for sampling bias'' \& `` the respondents to 
the survey may not be representative of the target population. ''

* Describe  and motive  method  for analyzing the data

@@

>>>>

The purpose of this survey study is therefore to test what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

The purpose of this survey study is therefore to find what are the differences in readability between five common and well known programming languages. With the aim of developing a metric to describe the readability of a given program, which takes into account the inherent readability of the language in which it is written.
\newline

@@

\begin{tabular}{| l | r | c |}
	\hline
	\textbf{Variable Name} & \textbf{Research Question} & \textbf{Item on Survey} \\ \hline
	Occupation & RQ1, SQ1 & \\ \hline
	Experience & RQ1, SQ1 & \\ \hline
	Preferred Language & RQ1, SQ2 & \\ \hline
	Least Preferred Language & RQ1, SQ2& \\  \hline
	Working Language & RQ1, SQ2 & \\ 
	\hline
	\end{tabular}
%------------------------------------------------------------------------- 
\Section{Methodology}
The main purpose of this study is to discover differences in the perceived readability of code. The study will be carried out in three phases. In phase 1, we will identify the target population. In phase 2, the survey will be designed and carried out. In phase 3, the results will be analysed. The investigation method will be in the form of a questionnaire. The main argument for the questionnaire is that the survey must be distributed to a large amount of people. A quantitative is also well-suited for this study since there are no existing publications that explore readability differences between languages.

\SubSection{Identifying the Population}
As mentioned before, the goal of this study is to identify the inherent differences in readability of programming languages. To research this, a broad population is required, since there may be strong correlation between the perception of readability and the previously defined independent variables. As such, a research survey will be conducted. This reasoning is reinforced by Easterbrook et al. \cite{easterbrook2008selecting} who state ``Survey research is used to identify the characteristics of a broad population of individuals''.

* Describe  and explain the research  strategy (i.e.  Survey/Questionnaire)
and investigation methods that  will  be  used  for the study.  Motivate  your  
choice  of  survey/questionnaire  using relevant  references.
\newline

\SubSection{Questionnaire}
Blabla

\SubSection{Results Analysis}

We will use a survey/questionnaire to collect the data.
Sampling - ID a small subset of the entire population
\newline

* Describe  data  collection  procedures, sampling  method(s),  number  of  
subjects, response  rate  etc.
\newline

Random sampling from 200 people(guess). Sample 10\%, collect online via survey, Response rate of 15/20 (75\%)
\newline

Sampling bias - What we might face, how we overcome. State which threats and how they were minimised
\newline

* Create  questions for your  survey  (include  the questions in  your  report)
%Table goes here
\newline

* Describe  the population  and size  of  population
\newline
The population will be software developers in the SEM program. This includes teachers, students, professionals and hobbyists. Lets say the sample is 20 persons from the whole of SEM, 1st, 2nd, 3rd and staff.
\newline
\cite{easterbrook2008selecting} - ``A major challenge in survey research is to control for sampling bias'' \& `` the respondents to 
the survey may not be representative of the target population. ''
\newline

* Describe  and motive  method  for analyzing the data
\newline

@@

\SubSection{Literature Review}
The first phase will include a literature review. The main goal is to review previously published papers which are related to code readability. The existing studies will serve as a foundation for our study, as the goal of our study is not to further develop or research code readability, but compare readability between languages (using academia's existing definition of readability). The review will also serve as a base for the second phase, where the target population will be decided. 
\newline

In phase 1, an initial literature review will be conducted. The aim is to cover previously published studies to be able to provide a study which is purposeful for academia.
